---
title: "Report"
author: "Claudia Tang, Jacopo Malatesta"
date: "25/1/2020"
output: 
  html_document:
    toc: true
    theme: spacelab
    highlight: pygments
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = F)
```

## Loading the packages

```{r,message=FALSE}
library(RCurl); library(rvest); library(tidyverse); library(stringr)

```


## Point 1 

Inspecting the robots.txt file

```{r}
browseURL("http://beppegrillo.it/robots.txt") 
```

The first line we read says: "User-agent: *". This simply means that the following instructions apply to all robots.

The following two lines are "Disallow: /wp-admin/" and "Allow: /wp-admin/admin-ajax.php". They are telling us that the site is blocking the wp-admin folder with the exception of the admin-ajax.php file. In other words, we are not allowed to download any page from that folder with the exception of the admin-ajax.php file. 



## Point 2

Storing our URL link into an object called url 

```{r}
url <- "http://www.beppegrillo.it/un-mare-di-plastica-ci-sommergera/"

```

Downloading the page using RCcurl::getURL() while informing the webmaster about my browser details and my e-mail address.

```{r}
page <- getURL(url, 
               useragent = str_c(R.version$platform,
                                 R.version$version.string,
                                 sep = ", "),
               httpheader = c(From = "jacopomalatesta95@gmail.com")) 

```


Saving the page in my directory

```{r}
writeLines(page, 
           con = here::here("downloaded_pages", "beppe_grillo_plastica.html")) 

```


## Point 3

Downloading all the links in the page 

```{r}
links <- XML::getHTMLLinks( here::here("downloaded_pages","beppe_grillo_plastica.html"))

```

Creating a tibble to store all the links

```{r}
dat <- tibble(
  links = links
)
dat

```

Selecting all the links re-directing to other posts from the beppegrillo.it blog

```{r}
internal_links <- str_subset(links, "^http://www\\.beppegrillo\\.it")

```

Creating a tibble with all the links re-directing to other posts from the beppegrillo.it blog

```{r}
dat2 <- tibble(
  links = internal_links
)

dat2

```


Same thing, this time with rvest

```{r}
links_rvest <- read_html(here::here("downloaded_pages", "beppe_grillo_plastica.html")) %>% 
  html_nodes(css = "a") %>% 
  html_attr("href")

```


Creating a dataframe containing the links

```{r}
dat3 <- tibble(
  links = links_rvest
)

dat3

```


Selecting all the links re-directing to other posts from the beppegrillo.it blog

```{r}
internal_links_rvest <- str_subset(links, "^http://www\\.beppegrillo\\.it")

```

Creating a dataframe containing the links re-directing to other posts from the beppegrillo.it blog

```{r}
dat4 <- tibble(
  links = internal_links_rvest
)

dat4
```


## Point 4
Scraping the link of "prossimo articolo"
```{r}
prossimo_link <- read_html(here::here("downloaded_pages", "beppe_grillo_plastica.html")) %>% 
  html_nodes(".td-post-next-post a") %>% html_attr("href")
prossimo_link
```

Downloading the page of following article
```{r}
download.file(prossimo_link,destfile = here::here("downloaded_pages", "prossimo_articolo.html"))
```

Scraping the text of the article
```{r}
articolo <- read_html(here::here("downloaded_pages","prossimo_articolo.html")) %>%
  html_nodes("p:nth-child(5) , p:nth-child(3) , p:nth-child(2) , p:nth-child(1) , .td-pb-padding-side .entry-title") %>%   html_text()
articolo <- articolo[1:5]
articolo
```

### How to use previous and following links to scrape more post?
1. First, creating a loop to get the previous links and following links. The times of iteration are based on
how many previous and following articles you'd like to scrape.
For example, we set "http://www.beppegrillo.it/un-mare-di-plastica-ci-sommergera/" as our initial page, and we want to
scrape 4 following pages: 
```{r}
all_prossimo_links <-vector(mode = "character", length = 5)    
dir.create(here::here("downloaded_pages/prossimo articolo"))    
all_prossimo_links [[1]] <- "http://www.beppegrillo.it/un-mare-di-plastica-ci-sommergera/"      
for (i in 1:4) {   
  all_prossimo_links[[i+1]] <- read_html(all_prossimo_links[i]) %>% html_nodes(".td-post-next-post a") %>%     html_attr("href")     
  Sys.sleep(2)    
}    
```
2. Downloading the pages and scraping the text 
```{r}
article_description <-list()    
for (i in 1:5) {       
  file_path <- here::here("downloaded_pages/prossimo articolo",str_c("article_", i, ".html"))       
  download.file(all_prossimo_link[[i]],destfile =file_path)     
  article_description[[i]] <- read_html(file_path) %>%       
    html_nodes("p") %>%           
    html_text()         
  Sys.sleep(2)       
}       
```
3. Scraping the previous links and articles is the same, just to replace the css path in the first with ".td-post-next-prev-content a" 


## Point 5
### 1. Getting the links of 47 pages 
```{r}
archivepages <-list()
url2016 <- "https://www.beppegrillo.it/category/archivio/2016/"
archivepages[[1]] <- url2016
for (i in 1:45) {
  cat("iteration_",i,"\n")
  archivepages[[i+1]] <- read_html(archivepages[[i]]) %>% html_nodes(".last+ a") %>% html_attr("href") 
  Sys.sleep(2)
}
```

The css path of "next page" on the 46th page is different, so archivepages[[47]] is empty, we repalce it with the right URL
```{r}
archivepages[[47]] <- "https://www.beppegrillo.it/category/archivio/2016/page/47/"
```

### 2. Getting all the articles links on 47 pages
```{r}
articlelinks <- list()
for (i in 1:46) {
  cat("iteration_",i)
  articlelinks[(1+(i-1)*10):(i*10)] <- read_html(archivepages[[i]]) %>%
    html_nodes(".td_module_10 .td-module-title a") %>% html_attr("href") 
  Sys.sleep(2)
}
```

```{r}
articlelinks[461:469] <- read_html(archivepages[[47]]) %>%
    html_nodes(".td_module_10 .td-module-title a") %>% html_attr("href")
head(articlelinks)
```

### 3. Downloading all the article pages
```{r}
dir.create(here::here("downloaded_pages/articles"))
for (i in 55:149) {
  cat("Iteration:", i,"\n")
  filepath2 <- here::here("downloaded_pages/articles",str_c("page_", i, ".html"))
  download.file(articlelinks[[i]], filepath2)
  Sys.sleep(2) }

articlelinks[[150]] <- NULL
```

```{r}
for (i in 150:211) {
  cat("Iteration:", i,"\n")
  filepath2 <- here::here("downloaded_pages/articles",str_c("page_", i, ".html"))
  download.file(articlelinks[[i]], filepath2)
  Sys.sleep(2) }

articlelinks[[212]] <- NULL
```

```{r}
for (i in 212:417) {
  cat("Iteration:", i,"\n")
  filepath2 <- here::here("downloaded_pages/articles",str_c("page_", i, ".html"))
  download.file(articlelinks[[i]], filepath2)
  Sys.sleep(2) }

articlelinks[[418]] <- NULL
```

```{r}
for (i in 418:466) {
  cat("Iteration:", i,"\n")
  filepath2 <- here::here("downloaded_pages/articles",str_c("page_", i, ".html"))
  download.file(articlelinks[[i]], filepath2)
  Sys.sleep(2) }
```

### 4.Scraping the text

```{r}
text <- list()
for (i in 1:466) {
  cat("Iteration:", i,"\n")
  filepath3 <- here::here("downloaded_pages/articles",str_c("page_", i, ".html"))
  text[[i]] <- read_html(filepath3) %>%
    html_nodes("p") %>% 
    html_text() }
```


## Point 6
### What is crawling?
Crawling means looking at all the content and codes on a page, analyzing and downloading them. This can be done for 
different purposes, the main one being web indexing. A web spider is a program that automatically browses and downloads Web pages by following hyperlinks in a methodical and automated manner. They are usually used for web indexing, but 
can also be used for web scraping. 

### Building a spider scraper
The function we use to build the scraper spider is Rcrawler   
Arguments: 1.Website: to idicate the website   
2. Obeyrobots: if TRUE, the crawler will parse the website’s robots.txt file and obey its ruhow many processes will execute the taskles allowed and disallowed directories.   
3. ExtractCSSPat: to extract one element per pattern for every page       
4. ManyPerPattern: to extract multiple elements per pattern, we need to set ManyPerPattern = T        
5. no_cores: specify how many processes will execute the task       
6. no_conn: specify how many HTTP requests will be sent simultaneously (in parallel).            

